---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# rearrvisr

The R package rearrvisr provides functions to identify and visualize inter- and
intrachromosomal translocations and inversions between a focal genome and an
ancestral genome reconstruction, or two extant genomes. Rearrangements,
breakpoints, and synteny blocks are identified along the focal genome and output
in a tabular format. Rearrangements and synteny blocks can be visualized along
the focal genome by two graphical functions.


## Installation

You can install rearrvisr from GitHub using the devtools package:

``` r
## install and load devtools
install.packages("devtools")
library(devtools)

## install and load rearrvisr
install_github("dorolin/rearrvisr")
library(rearrvisr)
```

## Example

For a brief overview of the functionalities of the package, type

```{r example, message=FALSE, eval=FALSE}
?rearrvisr
```

A more detailed description of the package functions and a tutorial is provided in the package vignette.
